---
title: "Assignment 2"
author: "Pavlo Nikitenko(3049843), Chiara Sauren(3050345), Viktor Stoppel(3004345)"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
deadline: 06.07.22
fontsize: 11pt
classoption: a4paper
supervisor: Martin Arnold, Jens Klenke
always_allow_html: yes
---
Make sure to install and load following packages first:
```{r, echo= T, message= FALSE, include= T, eval=TRUE, warning =FALSE}
library(profvis)
library(purrr)
library(tibble)

```

## 1)

a) A function to calculate the loglikelihood negative binomial distribution.

```{r}

lprob_nbinomial<-function(p, x){
  (-sum(log(choose(x+10-1, x))+10*log(p)+x*log(1-p)))
}

```

Generate some example data to test and profile the function:


```{r}

x <- rnbinom( n = 1e5, size = 5, prob = .2)
x <- rnbinom( n = 1e6, size = 5, prob = .2)
length(x)

```

Profile collecting of example data and parts of the function in comparison
  
```{r, warnings = F, message=FALSE}
profvis({
  
  test <-  (-sum((log(choose(x+10-1, x)))+ 10 * log(0.5)+x * log(1-0.5)))
  
})

```

With increasing length of the example data x, the computation time increases
accordingly. With n = 100000 (1e5) observations the lprob_nbinomial() function takes up
to 10 ms, using up 2.3 mbit of memory space. With n = 1000000 (1e6) the computation 
time already takes 110 ms and takes up to 22.9 mbits of memory space.

b)


Ephemeral environments are meant to serve as a testing, temporary or dynamic environment
that show a replica of the actual work-environment. They usually use replicated data and
test whether a test or step is applicable before risking on damaging the real work environment.
They help in accelerating the programming or software development cycle, limiting the need to
rework broad parts of the written code.
In comparison to a ephemeral environment, the function factory 
encloses the environment of the manufactured function. This serves as the execution
environment of the function factory.

c) Function factory:

```{r}
ll_nbinomial<-function(x){
  function(p){
    (-sum(log(choose(x+10-1, x))+10*log(p)+x*log(1-p)))
  }
}


```

d)  Test of the function factory with pseudo-random numbers x1

```{r}
set.seed(123)
x1<-rnbinom(n=1e3, size = 10, prob = .3)

# Test the function
ll<-ll_nbinomial(x1)
ll(0.2)
```

e) function that obtains the MLE:

```{r, warning = FALSE}
nbin_mle<-function(x){
mle <-  list(optim(par = 0,fn=ll ,lower = 1e-8,
        upper = 1-1e-8))
return(mle)
}
#test function
nbin_mle(x1)

#alternative way

mle_a<-optimize(ll, interval = c(0,1))
mle_a
```

f) Implement a summary method for the output of nbin_mle

```{r}
nbin_mle<-function(x){
  mle <-  list(optim(par = 0,fn=ll ,lower = 1e-8,
                     upper = 1-1e-8, method = "L-BFGS-B"))
  class(mle)<-"my_mle"
  return(mle)
}


nbin_mle(x1)

nbin_mle(x1)[[1]]$par

summary.my_mle <- function(x) {
  if(class(x) == "my_mle") {
    x <- unlist(x)
    out <<- list(
      name = quote(x),
      min = min(x),
      tibble(
        prob=seq(0,1,0.01)),
      ll=my_nbin_mle[[1]]$par,
      MLE=my_nbin_mle[[1]]$value,
      counts=my_nbin_mle[[1]]$counts
    )
    class(out) <- "summary.my_mle"
    return(out)
  } else {
    message("Object not of class my_mle!")
  }
}

my_nbin_mle<-nbin_mle(x1)
summary(my_nbin_mle)
```

g) print and plot method for objects of class summary.my_mle:

```{r}
# print method
print.summary.my_mle <- function(x) {
  if(class(x) == "summary.my_mle") {
    cat(
      "Summary for", x$name, ":\n\n",
      "Probabilities for MLE", my_nbin_mle[[1]]$value, "for", my_nbin_mle[[1]]$par
    )
  } else {
    message("Object not of class summary.my_mle!")
  }
  
}

summary(my_nbin_mle)

# plot method
plot.summary.my_mle <- function(x){
 pi <- (1:99)/100
loglikelihood <- sapply(pi, ll)
plot(pi, loglikelihood, type = "l",
     xlab = "Pi", ylab = "-log L(pi; x, k =10")
points(y =my_nbin_mle[[1]]$value,x=my_nbin_mle[[1]]$par,
      col="red", type = "p", lwd=2)

  
}
```
 
h) Demonstration with example data from d)
 
```{r}
summary(my_nbin_mle)

plot.summary.my_mle(x1)

```

