---
title: "R Assignment 1"
author: "Pavlo N., Chiara S., Viktor S."
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load packages, echo=FALSE, include=FALSE}
library(dplyr)
library(knitr)
library(stringr)
library(here)
library(stringi)
library(janitor)
library(magrittr)
library(lubridate)
library(tibble)
library(kableExtra)
library(ggplot2)
library(zoo)
library(stargazer)
library(modelr)
library(tidyr)
library(tidyverse)
library(rvest)
library(DBI)
library(RSQLite)

```

# Excercise 2

a)

load the immowelt data into R

```{r}
load(here::here("rent_advertisements.RData"))
```

omit column "heating_cost_excluded" as it contains no data (NAs) :

```{r}
immowelt %<>%
  select(-heating_cost_excluded)

head(immowelt)
names(immowelt) 

```

overview of the data:

```{r}
immowelt %>%
  knitr::kable(booktabs = TRUE, linesep = "",
               escape = TRUE, caption = 'Immowelt'
  ) |>
  kableExtra::kable_styling(font_size = 10,
                            latex_options = c("striped", "hold_position")) %>%
  kableExtra::row_spec(0, bold = TRUE)
```

Clean all non-available data (NA).

```{r}
immowelt_clean <- na.omit(immowelt)
immowelt_clean
```


Ensure that all variables of the dataset are stored using a proper class.

```{r}
char_v <- c("title","building_year")

immowelt_clean %<>%
  mutate(across(where(is.character) &! any_of(char_v),
                as.factor))

immowelt_clean %<>%
  mutate(building_year = as.numeric(building_year))
```

b) Calculate the cold_rent and warm_rent per square meter:

```{r}
immowelt_clean %<>%
  mutate(cold_rent_qm = cold_rent / square_meter) %>%
  mutate(warm_rent_qm = warm_rent / square_meter)

immowelt_clean$cold_rent_qm
immowelt_clean$warm_rent_qm
```


Create one table with the five districts with the most ads for each city:

```{r}
ads_essen <- immowelt_clean %>%
  filter(city =="essen") %>% 
  group_by(zipcode) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  slice(1:5)

ads_bochum <- immowelt_clean%>%
  filter(city=="bochum")%>% 
  group_by(zipcode)%>%
  summarise(count=n())%>%
  arrange(desc(count))%>%
  slice(1:5)

full_join(ads_bochum,ads_essen)  
```


d) Create a boxplot for the ten districts you found in (c), mapping the warm_rent.

```{r}
 immowelt_clean %>%
  mutate(zipcode = factor(zipcode, c("45141","45147","45279","45326","45355",
                                   "44793","44795","44866","44809","44801"))) %>%
  drop_na() %>%
  ggplot(aes(x=zipcode, y=warm_rent, color=city)) +
  geom_boxplot() +
  labs(title = 'Boxplot for the ten district with the most ads for essen and bochum',
       x ="\n Zipcode", y ="\n warm rent")+
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

e) Create a scatterplot showing the relationship between square_meter and cold_rent and warm_-
rent per square meter separately. Color and shape the points differently for the two cities. Also,
draw a regression line to point out the relationship in the plots.

```{r}
 immowelt_clean %>%
  ggplot(aes(x = square_meter, y = cold_rent_qm, color = city)) +
  geom_point() +
  geom_smooth(se=FALSE) +
  labs(title = "Relatonship between square meter and warm rent per square meter",
       x ="square meter", y ="cold rent per qm")

immowelt_clean %>%
  ggplot(aes(x = square_meter, y = warm_rent_qm, color = city)) +
  geom_point() +
  geom_smooth(se=FALSE) +
  labs(title = "Relatonship between square meter and warm rent per square meter",
       x="square meter", y="warm rent per qm")
```

f) To compare the housing market of the two cities graphically, create a boxplot on which both the
cold_rent and the warm_rent are plotted. Do this for the absolute rents as well as for the rents
per square meter.

```{r}
immowelt_clean%>%
  ggplot(aes(x=cold_rent,y=warm_rent, color=city))+
  geom_boxplot()+
  labs(title = "Comparing absolut warm Rent vs. cold Rent for Bochum and Essen",
       x="Cold rent",y="Warm rent" )

immowelt_clean%>%
  ggplot(aes(x=cold_rent_qm, y=warm_rent_qm, color=city))+
  geom_boxplot()+
  labs(title = "Comparing warm Rent vs. cold Rent per square meter for Bochum and Essen",
       x ="Cold rent per qm", y = "Warm rent per qm")
```

g) Calculate the share of Nebenkosten (Nebenkosten = service_charges + heating_cost_-
included) of the warm_rent and plot the percentage against the apartment size.

```{r}
immowelt_clean %>%
  select(heating_cost_included, square_meter, warm_rent) %>%
  mutate(share_nebenkosten = (heating_cost_included+immowelt_clean$service_charges)
         /warm_rent*100) %>%
  ggplot(aes(x=square_meter, y=share_nebenkosten))+
  geom_point()+
  labs(title = " Share of Nebenkosten of the warm rent",
       x="Appartment size in square meter", y="Share in %")
```

h) Next, you want to get an overview of the different efficiency classes of efficiency_class. Create
appropriate plots and compute statistics (if necessary) to answer the following questions:

i) Do the efficiency classes differ in terms of their energy demand? Discuss your findings shortly:

```{r}
immowelt_clean %>%
  select(efficiency_class,energy_demand, city)%>%
  mutate(efficiency_class = factor(efficiency_class,c(
    "A","A+","B","C","D","E",
    "F","G","H"))) %>%
  drop_na() %>%
  ggplot(aes(efficiency_class, energy_demand, color = city))+
  geom_point()
```

efficiency classes differ in terms of their energy demand. Low energy classes seem to correlate with high energy demand. High energy classes seem to correlate with low energy demands.

ii) How is the amount of ads distributed among the efficiency classes?

```{r}
immowelt_clean %>%
  select(efficiency_class, city)%>%
  drop_na()%>%
  mutate(efficiency_class=factor(efficiency_class,c(
    "A","A+","B","C","D","E",
    "F","G","H"))) %>%
  ggplot(aes(x=efficiency_class))+
  geom_bar(stat = 'count', width = 0.5, fill = '#004c93')+
  labs(title = "Amount of adds among the efficiency classes",
       x=" energy class", "amount", y = "ad count")
```

most ads are distributed at energy class "D".

iii) + vi)

```{r}
cor<-immowelt_clean %>%
  mutate(across(where(is.character), as.numeric))%>%
  mutate(across(where(is.factor), as.numeric))%>%
  select_if(is.numeric) %>%
  select(-title) %>%
  cor()

cor%>%
  as_tibble() %>%
  mutate(var1 = colnames(cor))%>%
  pivot_longer(-var1, names_to = "var2", values_to = "value")%>%
  ggplot(aes(var1, var2, fill=value))+
  geom_tile()
cor
cor[11,10]
cor[11,3]
```
correlation between effiency_class and building_year = -0.3325452. The correlation between effiency_class and cold_rent= -0.14201658.In both cases, theres a slight negative correlation. The whole dataset is included in this calculation.

In the following the variables "building year", "cold rent" and "efficiency class" will be considered for calculating the correlation:


```{r}
cor<-immowelt_clean%>%
  select(efficiency_class, building_year, cold_rent)%>%
  mutate(across(where(is.character), as.numeric))%>%
  mutate(across(where(is.factor), as.numeric))%>%
  select_if(is.numeric) %>%
  cor()

cor%>%
  as_tibble()%>%
  mutate(var1=colnames(cor))%>%
  pivot_longer(-var1, names_to = "var2", values_to = "value")%>%
  ggplot(aes(var1, var2, fill=value))+
  geom_tile()
cor
cor[1,2]  
cor[1,3]
```
The results do not differ. a slight negative correlation between the efficiency class and the building
year could be explained by improved building structure and heat efficient heating systems. It´s logical to assume that with decreasing building year,the efficiency class will rise to a better grading.
The same argumentation can be applied to the correlation between the efficiency class and the cold rent. A well build and innovative house will generally cost a higher cold rent which results in better insulation and hence a lower (= better) efficiency class.

i) Perform two linear regressions to predict warm_rent. Both regressions use the variables efficiency_-
class, rooms, building_year, square_meter, and service_charges. To investigate a systematical
difference between the cities, use the variable city in the first regression, and zipcode in the
other. Also, discuss why you cannot use city and zipcode in one regression and the advantages
of each approach.

```{r}
 reg1<-lm(warm_rent~efficiency_class+rooms+building_year+square_meter+service_charges+city,
         data = immowelt_clean)
summary(reg1) 

reg2<-lm(warm_rent~efficiency_class+rooms+building_year+square_meter+service_charges+zipcode,
         data = immowelt_clean)
summary(reg2)

reg3<-lm(warm_rent~efficiency_class+rooms+building_year+square_meter+service_charges+zipcode+city,
         data = immowelt_clean)
summary(reg3)  # for comparison
```

If both zipcode and city are used in the regression analysis, it might result in multicolinearity, which will lead to possibly reduced accuracy of the predictions.
To determine which model is more fitting, cross validation is used in the following:

```{r}
set.seed(123)
train<-immowelt_clean%>%
  slice_sample(prop = 0.8)

test<-immowelt_clean%>%
  anti_join(train)

mod_city<-lm(warm_rent~efficiency_class+rooms+building_year+square_meter+service_charges+city,
             data = train)
summary(mod_city) 

mod_zipcode<-lm(warm_rent~efficiency_class+rooms+building_year+square_meter+service_charges+zipcode,
                data = train)

summary(mod_zipcode)
```

For both models, compute the RMSE on the ‘test‘ dataset:

```{r}
 test%>%
  rmse(mod_city,.)

test%>%
  rmse(mod_zipcode,.)
```

The prediction with the variable "zipcode" is a better fit.

```{r}
mod_full<-lm(warm_rent~efficiency_class+rooms+building_year+square_meter+service_charges+
               zipcode+city, data = train)
 test%>%
  rmse(mod_full,.)

summary(mod_full)
summary(mod_city)
summary(mod_zipcode)
```

"Mod__full" has to much impact. A possible explanation could be multicollinearity due to using
the variable "zipcode" and "city" in the same regression.

# Exercise 3

a) Create a function that uses a standard ggplot2 theme and customize the following elements
according to your taste.


```{r}

 theme_favourite <- function(){
  theme_classic() %+replace%
    theme(
      text = element_text(family = "serif", size = 16),
      panel.spacing = unit(2, "cm"),
      panel.grid.major = element_line(colour = "blue"),
      panel.grid.minor = element_line(color = "blue")
      
    )
}
```

b) Write a function ggscatt() that generates a scatter plot. The function should be able to create
faceted plots. Your theme from (a) should be used.

```{r}
ggscatt <- function(data,x,y){
  ggplot(data, aes(x = x, y=y)) +
    geom_point() +
    theme_favourite()+
    labs(title = "A scatter plot") +
    facet_grid()
}
```

c) Establish a relative connection to the database.

```{r}
library(dplyr)
connection <- DBI::dbConnect(
  drv = RSQLite::SQLite(),
  dbname = here::here("assignment_1.sqlite3"),
)
# show the list of tables in the database
DBI::dbListTables(connection)
```

d) Load the table metro into R.

```{r}
# create an object which is a reference to a table in the database
 metro<-tbl(connection, "metro")
head(metro)

#actually pull the data into R.
metro_R<-metro %>% 
  collect(n=Inf)
head(metro_R)
```

e) Ensure that all variables are stored using a proper class.

```{r}
 metro_R%<>%
  mutate(date_time=as_datetime(date_time))
tail(metro_R)
```

f) create a new variable weekday that represents the weekdays.

```{r}
 metro_R %<>%
  mutate(weekday=weekdays(date_time))

```

g) Use your function ggscatt() from (b).

```{r}
ggscatt(data = metro_R, metro_R$traffic_volume, metro_R$temp)
ggscatt(data = metro_R, metro_R$traffic_volume, metro_R$rain_1h)
ggscatt(data = metro_R, metro_R$traffic_volume, metro_R$snow_1h)
ggscatt(data = metro_R, metro_R$traffic_volume, metro_R$clouds_all)
```

h) Create a boxplot with the variable weekday on the x-axis and traffic_volume on the y-axis.

```{r}
metro_R %>%
  mutate(weekday=factor(weekday, c("Montag","Dienstag","Mittwoch","Donnerstag","Freitag",
                                   "Samstag","Sonntag"))) %>%
  ggplot(aes(x=weekday, y=traffic_volume))+
  geom_boxplot(color="steelblue")+
  labs(title = "Boxplot of traffic volume and Weekday", 
       x="Weekday", y="traffic Volume")
```
 
 i) Add your modified dataframe as a table to the database under the same metro_2.
 
```{r}
#dbWriteTable(connection,
                  #name="metro_2",
                  #value=metro_R)
               
#db_list_tables(connection)
```
 
# Exercise No. 4)

a) 

 $ git rm byeGit.txt  # removing and staging removal of byeGit.txt

$ git add HelloGit.txt  # staging for commit

$ git status  # make sure HelloGit.txt and byeGit.txt are staged

$ git commit -m "Fixes to file"    # HelloGit.txt committed

$ git add assignment_1.sqlite3     # track files for staging
$ git add rent_advertisment.RData  

$ git commit -m "data added"   # committed files

b)

 $ git add -p HelloGit.txt ## break down file into hunks, Git will prompt you 
                          ## with a choice which hunks to stage for next commit
$ git commit -m "Part 1"

$ git add HelloGit.txt  ## stage rest of commitment

$ git commit -m "Part2" ## commit rest of commitment

